On Devon Allen's Disqualification at the 2022 Track and Field World Championship

### 2023-04-21 Manuscript/manuscript.tex
comments

\subsection{GLMM} \label{subsec:Results_GLMM}
%Section 4.1: Gamma model results show the fitting with and without 2022,
%talk about p values and thresholds from the simulations (do not include the
%results in the methods section).

\jy{present the estimated parameters first before deriving the p-value using the
  estimated parameters. The difference in variance of the random effects using
  different data motivated the rank-based study.}

@@

\begin{table}
  \centering
  \begin{tabular}{c c c c c c}
      \toprule
      Dataset & Venue standard error & Int effect est & Int se & Int var & Resid Var \\
      \midrule
      Older Finals & 0.0439 & $-1.901$ & 0.0251 & 0.0019 & 0.0109 \\
      All Finals & 0.0504 & $-1.914$ & 0.0280 & 0.0025 & 0.0112 \\
      Older Pooled & 0.0495 & $-1.853$ & 0.0305 & 0.0024 & 0.0243 \\
      All Pooled & 0.0554 & $-1.869$ & 0.0348 & 0.0031 & 0.0235 \\
      \bottomrule
  \end{tabular}
  \caption{Summary statistics for the GLMM on various data sets}
  \label{tab:Gamma_parameters}
\end{table}

At a size of $n=10,000,000$, the calculated probability of a reaction
time being below 0.1 seconds was as follows for the various different data sets:
\jy{label the table and reference to it; clean it up}
\begin{table}
  \centering
  \begin{tabular}{c c c c} 
   \toprule
   Data Set & P(RxnTime $<$ 0.1) & P(RxnTime $<$ 0.09) & P(RxnTime $<$ 0.08) \\ 
   \midrule
   all finals gamma log & $8.56\cdot10^{-4}$ & $4.1\cdot10^{-5}$ & $6.0\cdot10^{-7}$ \\ 
   old finals gamma log & $4.39\cdot10^{-4}$ & $1.63\cdot10^{-5}$ & $2.0\cdot10^{-5}$ \\
   all pooled gamma log & $6.86\cdot10^{-3}$ & $1.21\cdot10^{-3}$ & $1.3\cdot10^{-4}$ \\
   old pooled gamma log & $5.76\cdot10^{-3}$ & $9.93\cdot10^{-4}$ & $1.0\cdot10^{-4}$\\
   \bottomrule
  \end{tabular}
  \caption{Probabilities of observing reaction times less than 0.1, 0.09, and
  0.08 for various data sets}
  \label{tab:Sim_probability}
\end{table}

@@

\subsection{Rank-based Comparison} \label{subsec:Results_Rank}
%Section 4.2 is motivated by seiko timing and look at same athletes across
%multiple types of competition: 2019 and national

%Discussion/Conclusion is beyond results.  Limitations, what type of data we
%hope to have.

@@

As Seiko timed both events, there should not be a significant
difference if the timing equipment in both instances was working correctly.
  To put it simply, there is not a reasonable explanation for 
this. It is inconceivable that so many athletes would improve such a significant
amount in such a small amount of time. 6 countries are represented in this 
comparison, which drastically decreases the chances of this issue being caused by
one specific country.  The United States athlete's improvement in times was
discussed earlier in the paper, but this data shows that on average there was
%Use a reference in this part
improvement for British, Polish, French, Brazilian, and Spanish athletes.

@@

\section{Appendix}
\label{sec:Appendix}
%Put downloadable data spreadsheet
Here is World Athletics website with the data: \url{https://www.worldathletics.org/results/world-athletics-championships}.
Here is the data for the USA Track and Field Championships: \url{https://www.flashresults.com/2022_Meets/Outdoor/06-23_USATF/}

For the pooled data set
\begin{center}
  \begin{tabular}{|c  c  c  c  c  c  c |}
   \hline 
   Model & AIC & Log Likelihood & Int effect est & Int se & Int var & Resid Var \\ [0.5ex] 
   \hline\hline
   linear one & -1667 & 835.5 & 0.1529 & 0.0014 & N/A & N/A \\
   \hline
   linear year & -1713 & 859.3 & 0.1541 & 0.0040 & 1.719e-04 & 5.926e-04 \\ 
   \hline
   gamma one & -1756 & 880.2 & 6.554 & 0.0598 & N/A & N/A \\
   \hline
   gamma year & -1848 & 926.9 & 6.553 & 0.2269 & 0.1305 & 0.0234 \\
   \hline
   gamma one log & -1756 & 880.2 & -1.880 & 0.0091 & N/A & N/A \\
   \hline
   gamma year log & -1848 & 927.0 & -1.869 & 0.0348 & 0.0031 & 0.0235 \\ [0.5ex]
   \hline
  \end{tabular}
  \end{center}

>>>>

\subsection{GLMM} \label{subsec:Results_GLMM}

\jy{motivate first why you want to run the analysis with and without the 2022 data.}

@@

\jy{Close captions with a period.}
\begin{table}
  \centering
  \begin{tabular}{c c c c c c}
      \toprule
      Dataset & Venue standard error & Int effect est & Int se & Int var & Resid Var \\
      \midrule
      Older Finals & 0.0439 & $-1.901$ & 0.0251 & 0.0019 & 0.0109 \\
      All Finals & 0.0504 & $-1.914$ & 0.0280 & 0.0025 & 0.0112 \\
      Older Pooled & 0.0495 & $-1.853$ & 0.0305 & 0.0024 & 0.0243 \\
      All Pooled & 0.0554 & $-1.869$ & 0.0348 & 0.0031 & 0.0235 \\
      \bottomrule
  \end{tabular}
  \caption{Summary statistics for the GLMM on various data sets}
  \label{tab:Gamma_parameters}
\end{table}

At a size of $n=10,000,000$, the calculated probability of a reaction
time being below 0.1 seconds was as follows for the various different data sets:
\jy{label the table and reference to it; clean it up}
\begin{table}
  \centering
  \begin{tabular}{c c c c} 
   \toprule
   Data Set & P(RxnTime $<$ 0.1) & P(RxnTime $<$ 0.09) & P(RxnTime $<$ 0.08) \\ 
   \midrule
   all finals & $8.56\cdot10^{-4}$ & $4.1\cdot10^{-5}$ & $6.0\cdot10^{-7}$ \\ 
   old finals & $4.39\cdot10^{-4}$ & $1.63\cdot10^{-5}$ & $2.0\cdot10^{-5}$ \\
   all pooled & $6.86\cdot10^{-3}$ & $1.21\cdot10^{-3}$ & $1.3\cdot10^{-4}$ \\
   old pooled & $5.76\cdot10^{-3}$ & $9.93\cdot10^{-4}$ & $1.0\cdot10^{-4}$\\
   \bottomrule
  \end{tabular}
  \caption{Probabilities of observing reaction times less than 0.1, 0.09, and
  0.08 for various data sets}
  \label{tab:Sim_probability}
\end{table}

@@

\subsection{Rank-based Comparison} \label{subsec:Results_Rank}

\jy{motivate first; describe the data (what are the grouping variables in the
  two data sets? use one paragraph for each.}

@@

As Seiko timed both events, there should not be a significant
difference if the timing equipment in both instances was working correctly.
  To put it simply, there is not a reasonable explanation for 
this. It is inconceivable that so many athletes would improve such a significant
amount in such a small amount of time. 6 countries are represented in this 
comparison, which drastically decreases the chances of this issue being caused by
one specific country.  The United States athlete's improvement in times was
discussed earlier in the paper, but this data shows that on average there was
\jy{any reference?}
improvement for British, Polish, French, Brazilian, and Spanish athletes.

@@

\section{Appendix}
\label{sec:Appendix}
%Put downloadable data spreadsheet
The World Championship data is available from the World Athletics website:
\url{https://www.worldathletics.org/results/world-athletics-championships}.

\jy{You have countries beyond USA}
Here is the data for the USA Track and Field Championships: \url{https://www.flashresults.com/2022_Meets/Outdoor/06-23_USATF/}
